\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-05-05 main.tex
going over appendix

The perfect memory assumption is not only unrealistic but it also creates this
curious inconsistency. This has lead us to question how robust is our
understanding of cooperation. In this work we explore whether direct
reciprocity can evolve if individuals only remember a minimum of social
information. Though we are not the first to question the assumptions of
estimating fitness~\cite{Roca2006}, we are the first to explore the effect
of payoff memory.

@@

We consider a pairwise comparison process. We assume a population of \(N\)
individuals (\(N\) is even) where at any point in time there are at most two
different strategies in present. There are \(k\) individuals who play the mutant
strategy and \(N - k\) individuals who play the resident strategy. Each step of
the evolutionary process consists of two stages; a game stage and an update
stage.

In the game stage, each individual is randomly matched with some other
individual in the population. Their interaction lasts for a number of turns
which is not fixed but depends on the continuation probability \(\delta\). At
each turn the individuals have choose between cooperation (C) and defection (D).
If both players cooperate they receive the reward payoff \(R\), whereas if both
players defect they receive the punishment payoff \(P\). If one cooperates but
the other defects, the defector receives the temptation to defect, \(T\),
whereas the cooperator receives the sucker's payoff, \(S\).

In this work we consider different social dilemmas represented by the harmony
game, the stag hunt game, the snowdrift or hawk-dove game, the prisoner's
dilemma, and a special case of the prisoner's dilemma, the donation game
(Table~\ref{table:social_dilemmas}).

\begin{table}[!htbp]
  \begin{center}
    \resizebox{.65\textwidth}{!}{
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{ccc}
  \toprule
  & \textbf{social dilemmas} & \textbf{payoffs' constrains} \\
  \midrule
(i) & stage hunt  & \(R > T > P > S\) \\
(ii) & snowdrift  & \(T > R > S > P\) \\
(iii) & harmony  & \(R > T > S > P\) \\
(iv) & prisoner dilemma  & \(T > R > P > S\) \\
(v)& donation game  & \(T > R > P > S\) \& \(T=b, R=b-c, S=-c, P=0\) \\
  \bottomrule
      \end{tabular}}
  \end{center}
  \caption{We present results on the all of the listed social dilemmas. The payoffs'
  constrains are different for each game.}
  \label{table:social_dilemmas}
\end{table}

Results for cases (i) - (iv) were presented in section~\ref{section:2_by_2_games}
and results for case (v) were presented in section~\ref{section:donation}.

A further assumption of our model is that individuals make use of reactive
strategies when they make decisions in each round. Reactive strategy are a set
of strategies that take into account only the previous action of the opponent.
A reactive strategy can be written explicitly as a vector,

@@

We iterate this basic evolutionary step until either the mutant strategy goes
extinct, or until it fixes in the population and becomes the new resident
strategy. After either outcome, we set $k$ to $1$ and we introduce a new mutant
strategy which is uniformly chosen from all reactive strategies at random.

This process of mutation and fixation/extinction is iterated many times.
Instead of simulating each step of the evolutionary process, we estimate
the probability that a newly introduced mutant fixes~\cite{nowak2004emergence}.
This is defined as the fixation probability of the mutant, and the standard
form is the following,

@@

This evolutionary process is summarized by Algorithm~\ref{algorithm:pairwise_comparison}.

\begin{algorithm}[!htbp]
  \SetAlgoLined
   $N \leftarrow$ population size\;
   $k \leftarrow 1$\;
   resident $\leftarrow (0, 0, 0)$\;
   \While{step $<$ maximum number of steps}{
    mutant $\leftarrow$ random: $\{\emptyset \}\ \rightarrow R^3$\;
    fixation probability $\leftarrow \varphi $\;
    \If{$\varphi >$ random: $i \rightarrow [0, 1]$}{
      resident $\leftarrow$ mutant;
     }}
     \caption{Pairwise comparison process}\label{algorithm:pairwise_comparison}
\end{algorithm}

The aim of this work is to explore the effect of updating memory on the
cooperation rate of the evolved population. For this reason we consider two
different approaches when estimating the payoffs at the updating stage. The two
approaches we consider are those of (i) the expected payoffs and (ii) the
stochastic payoffs.

@@

The expected payoffs are the conventional payoffs used in the updating
stage~\cite{imhof2010stochastic}. They are defined as the mean payoff an
individual in a well-mixed population that engages in repeated games with all
other population members.

We first define the payoff of two reactive strategies at the game stage. Assume
two reactive strategies $s_1\!=\!(y_1, p_1, q_1$) and $s_2\!=\!(y_2,p_2,q_2)$.
It is not necessary to simulate the play move by move. Instead the play between
the two strategies is defined a Markov matrix \(M\),

@@

whose stationary vector \(\mathbf{v}\), combined with the payoff \(U\), yields
the expected outcome for each strategy,
\(\langle\mathbf{v}(s_1,s_2),\mathbf{u}\rangle\).

% In each step
Given a population of \(N\) individual with \(k\) individuals playing the mutant
strategy, \(s_M = (y_M, p_M, q_M)\), and \(N -k\) playing the resident strategy,
\(s_R = (y_R, p_R, q_R)\), the expected payoffs of a resident \(\pi_R\) and of
a mutant strategy \(\pi_M\) are defined as,

\begin{equation} \label{Eq:ExpPay}
  \begin{array}{lcrcr}
  \displaystyle \pi_R	&=	&\displaystyle \frac{N\!-\!k\!-\!1}{N-1}\cdot \langle\mathbf{v}(s_R,s_R),\mathbf{U}\rangle	&+	&\displaystyle\frac{k}{N-1}\cdot \langle\mathbf{v}(s_R,s_M),\mathbf{U}\rangle,\\[0.5cm]
  \displaystyle \pi_M	&=	&\displaystyle\frac{N-k}{N-1}\cdot \langle\mathbf{v}(s_M,s_R),\mathbf{U}\rangle&+	&\displaystyle\frac{k-1}{N-1}\cdot \langle\mathbf{v}(s_M,s_M),\mathbf{U}\rangle.\\
  \end{array}
\end{equation}

Note that \(N\!-\!k\!-\!1\) is the number of other residents in the population,
and \(k\) is the number of residents. The payoffs are averaged by the number of
individuals in the population, given that interactions are not possible.
The same applies for the payoff of a mutant.

Given the expected payoff, the probabilities that the number of mutants
decreases and increases  (Equation~(\ref{eq:appendix_fixation_probability})),
are given by:

@@

\subsection*{Stochastic Payoffs}

We compare the expected payoffs with the finite memory payoffs which we refer to
as the stochastic payoffs. Initially, we consider the case of where the payoffs
correspond to the last round payoff an individual achieved after interacting
with one other individual.

The probability of being in any of the outcomes \(R, S, T, P\) in the last round
is given by Equation~(\ref{Eq:LastRound})
(Proposition~\ref{proposition:last_round}).

\begin{Prop}\label{proposition:last_round}
Assume a play between the reactive strategies \(s_1\) and \(s_2\) with a
continuation probability \(\delta\). Then the probability of being in any of the
four outcomes \(R, S, T, P\) are given by,

@@

  \mathbf{v}_{R}(S_1,S_2) &= &\displaystyle (1\!-\!\delta)\frac{y_1y_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(q_1+r_1\big((1\!-\!\delta)y_2+\delta q_2\big)\Big) \Big(q_2+r_2\big((1\!-\!\delta)y_1+\delta q_1\big)\Big)}
  {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)},\\[1cm]

  \mathbf{v}_{S}(S_1,S_2) &= &\displaystyle (1\!-\!\delta)\frac{y_1\bar{y}_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(q_1+r_1\big((1\!-\!\delta)y_2+\delta q_2\big)\Big) \Big(\bar{q}_2+\bar{r}_2\big((1\!-\!\delta)y_1+\delta p_1\big)\Big)}
  {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)},\\[1cm]

  \mathbf{v}_{T}(S_1,S_2) &= &\displaystyle (1\!-\!\delta)\frac{\bar{y}_1y_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(\bar{q}_1+\bar{r}_1\big((1\!-\!\delta)y_2+\delta p_2\big)\Big) \Big(q_2+r_2\big((1\!-\!\delta)y_1+\delta q_1\big)\Big)}
  {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)},\\[1cm]

  \mathbf{v}_{P}(S_1,S_2) &= &\displaystyle (1\!-\!\delta)\frac{\bar{y}_1\bar{y}_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(\bar{q}_1+\bar{r}_1\big((1\!-\!\delta)y_2+\delta p_2\big)\Big) \Big(\bar{q}_2+\bar{r}_2\big((1\!-\!\delta)y_1+\delta p_1\big)\Big)}
  {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)}.
  \end{array}
\end{equation}

In these expressions, we have used
the notation $r_i:=p_i\!-\!q_i$, $\bar{y}_i\!=\!1\!-\!y_i$, $\bar{q}_i:=1\!-\!q_i$,
and $\bar{r}_i:=\bar{p}_i\!-\!\bar{q}_i=-r_i$ for $i\!\in\!\{1,2\}$.
Let $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round,
and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector.
\end{Prop}

\begin{proof}
Given a play between two reactive strategies with continuation probability
$\delta$. The probability that the game ends on round \(t\) is given by,

\begin{equation}\label{eq:}
  (1 - \delta) \mathbf{v_0} \sum \delta^{t} M^{(t)}.
\end{equation}

Here, $\mathbf{v_0}$ denotes the expected distribution of the four outcomes in
the very first round, and \(1- \delta\) the probability that the game ends.
It can be shown that,

@@

and with some algebraic manipulation we derive to Equation~\ref{Eq:LastRound}.
\end{proof}

Considering that individuals can only interact with one other individual,
at that in each step a mutant and a resident are selected there are only five
possible pairings:

\begin{itemize}
  \item the selected resident is paired with the selected mutant
  \item the selected resident is paired with a resident and the selected mutant is paired with a resident
  \item the selected resident is paired with a resident and the selected mutant is paired with a mutant
  \item the selected resident is paired with a mutant and the selected mutant is paired with a resident
  \item the selected resident is paired with a mutant and the selected mutant is paired with a mutant
\end{itemize}

Each of the pairings happens with a given probability and that is illustrated
by Figure~\ref{fig:single_pairs}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.65\textwidth]{static/last_rounds_matches.tex}
  \caption{The tree}\label{fig:single_pairs}
\end{figure}

@@

% In these expressions, we have used the notation $r_i:=p_i\!-\!q_i$, $\bar{y}_i\!=\!1\!-\!y_i$, $\bar{q}_i:=1\!-\!q_i$, and $\bar{r}_i:=\bar{p}_i\!-\!\bar{q}_i=-r_i$ for $i\!\in\!\{1,2\}$. Let $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round, and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector. Then one can show the following result.

>>>>

The perfect memory assumption is not only unrealistic but it also creates this
curious inconsistency. This has led us to question how robust is our
understanding of cooperation. In this work we explore whether direct
reciprocity can evolve if individuals only remember a minimum of social
information. Though we are not the first to question the assumptions of
estimating fitness~\cite{Roca2006}, we are the first to explore the effect
of payoff memory.

@@

Consider a population of \(N\) individuals where \(N\) is even. At any point in
time there are at most two different strategies in present in the population.
More specifically, a mutant strategy played by \(k\) individuals and a resident
strategy played by \(N - k\) individuals. We assume a pairwise process in which
strategies spread because they are imitated more often. Each step of the
evolutionary process consists of two stages; a game stage and an update stage.

In the game stage, each individual is randomly matched with some other
individual in the population. Their interaction lasts for a number of turns
which is not fixed but depends on the continuation probability \(\delta\). At
each turn the individuals choose between cooperation (\(C\)) and defection
(\(D\)). Thus, there are four possible outcomes in each turn \(CC, CD, DC\) and
\(DD\). If both players cooperate they receive the reward payoff \(R\), whereas
if both players defect they receive the punishment payoff \(P\). If one
cooperates but the other defects, the defector receives the temptation to
defect, \(T\), whereas the cooperator receives the sucker's payoff, \(S\).
Let $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round,
and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector.

The values of the payoffs are not only based on the prisoner's dilemma but all
the symmetric \(2 \times 2\) games, Table~\ref{table:social_dilemmas}.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{.65\textwidth}{!}{
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{ccc}
  \toprule
  & \textbf{social dilemmas} & \textbf{payoffs' constrains} \\
  \midrule
(i) & stage hunt  & \(R > T > P > S\) \\
(ii) & snowdrift  & \(T > R > S > P\) \\
(iii) & harmony  & \(R > T > S > P\) \\
(iv) & prisoner dilemma  & \(T > R > P > S\) \\
(v)& donation game  & \(T > R > P > S\) \& \(T=b, R=b-c, S=-c, P=0\) \\
  \bottomrule
      \end{tabular}}
  \end{center}
  \caption{\textbf{Social dilemmas and payoffs' constrains}. The various social
  dilemmas we explore in this work. Results for cases (i) - (iv) were presented
  in section~\ref{section:2_by_2_games} and results for case (v) were presented
  in section~\ref{section:donation}.}
  \label{table:social_dilemmas}
\end{table}

A further assumption of our model is that individuals make use of reactive
strategies when they make decisions in each round. Reactive strategies are a set
of strategies that take into account only the previous action of the opponent.
A reactive strategy can be written explicitly as a vector,

@@

We iterate this basic evolutionary step until either the mutant strategy goes
extinct, or until it fixes in the population and becomes the new resident
strategy. After either outcome, we set $k$ to $1$ and we introduce a new mutant
strategy which is uniformly chosen from all reactive strategies at random.
Instead of simulating each step of the evolutionary process, we estimate the
probability that a newly introduced mutant fixes~\cite{nowak2004emergence}. This
is defined as the fixation probability of the mutant, and the standard form is
the following,

@@

This process of mutation and fixation/extinction is iterated many times. The
evolutionary process is summarized by
Algorithm~\ref{algorithm:pairwise_comparison}.

\begin{algorithm}[!htbp]
  \SetAlgoLined
   $N \leftarrow$ population size\;
   $k \leftarrow 1$\;
   resident $\leftarrow (0, 0, 0)$\;
   \While{step $<$ maximum number of steps}{
    mutant $\leftarrow$ random: $\{\emptyset \}\ \rightarrow R^3$\;
    fixation probability $\leftarrow \varphi $\;
    \If{$\varphi >$ random: $i \rightarrow [0, 1]$}{
      resident $\leftarrow$ mutant;
     }}
     \caption{Evolutionary process}\label{algorithm:pairwise_comparison}
\end{algorithm}

The aim of this work is to explore the effect of updating memory on the
cooperation rate of the evolved population. For this reason we consider two
different approaches when estimating the payoffs at the updating stage. The two
approaches we consider are those of (i) the expected and (ii) the limited memory
payoffs.

@@

The expected payoffs are the conventional payoffs used in the updating
stage~\cite{imhof2010stochastic}. They are defined as the mean payoff of an
individual in a well-mixed population that engages in repeated games with all
other population members.

We first define the payoff of two reactive strategies at the game stage. Assume
two reactive strategies $s_1\!=\!(y_1, p_1, q_1$) and $s_2\!=\!(y_2,p_2,q_2)$.
It is not necessary to simulate the play move by move, instead the play between
the two strategies is defined a Markov matrix \(M\),

@@

whose stationary vector \(\mathbf{v}\), combined with the payoff \(u\), yields
the game stage outcome for each strategy,
\(\langle\mathbf{v}(s_1,s_2),\mathbf{u}\rangle\)~\cite{Hauert1997}.

In the updating stage the learner adopts the strategy of the role model based on
their updating payoffs. Given that there are only two different types in the
population at each time step we only need to define the expected payoff for a
resident (\(\pi_R\)) and for a mutant (\(\pi_M\)). Assume the resident strategy
\(s_R = (y_R, p_R, q_R)\) and the mutant strategy \(s_M = (y_M, p_M, q_M)\), the
expected payoffs are give by,

\begin{equation} \label{Eq:ExpPay}
  \begin{array}{lcrcr}
  \displaystyle \pi_R	&=	&\displaystyle \frac{N\!-\!k\!-\!1}{N-1}\cdot \langle\mathbf{v}(s_R,s_R),\mathbf{u}\rangle	&+	&\displaystyle\frac{k}{N-1}\cdot \langle\mathbf{v}(s_R,s_M),\mathbf{u}\rangle,\\[0.5cm]
  \displaystyle \pi_M	&=	&\displaystyle\frac{N-k}{N-1}\cdot \langle\mathbf{v}(s_M,s_R),\mathbf{u}\rangle&+	&\displaystyle\frac{k-1}{N-1}\cdot \langle\mathbf{v}(s_M,s_M),\mathbf{u}\rangle.\\
  \end{array}
\end{equation}

The number of mutant in the population increase if a learner resident adopts the
strategy of a mutant role model, and decreases if a mutant leaner adopts the
strategy of a resident. The probabilities that the number of mutants decreases
and increases, \(\lambda^-_k\) and \(\lambda^+_k\), are not explicitly define
as,

@@

\subsection*{Limited memory payoffs}

Initially, we discuss the case of the last round updating payoff. At the stage
game we define the payoff of a reactive strategy in the last round,
Proposition~\ref{proposition:last_round}.

\begin{Prop}
    Consider a repeated prisoner's dilemma, with
    continuation probability $\delta$, between players with reactive strategies
    $s_1\!=\!(y_1, p_1, q_1$)  and $s_2\!=\!(y_2,p_2,q_2)$ respectively. Then the
    probability that the $s_1$ player receives the payoff $u\!\in\! \mathcal{U}$ in
    the very last round of the game is given by $v_{u}(s_1,s_2)$, as given by
    Equation~(\ref{Eq:LastRound}).

@@

      v_{R}(s_1,s_2) &= &\displaystyle (1\!-\!\delta)\frac{y_1y_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(q_1+r_1\big((1\!-\!\delta)y_2+\delta q_2\big)\Big) \Big(q_2+r_2\big((1\!-\!\delta)y_1+\delta q_1\big)\Big)}
      {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)} \times R,\\[1cm]

      v_{S}(s_1,s_2) &= &\displaystyle (1\!-\!\delta)\frac{y_1\bar{y}_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(q_1+r_1\big((1\!-\!\delta)y_2+\delta q_2\big)\Big) \Big(\bar{q}_2+\bar{r}_2\big((1\!-\!\delta)y_1+\delta p_1\big)\Big)}
      {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)} \times S,\\[1cm]

      v_{T}(s_1,s_2) &= &\displaystyle (1\!-\!\delta)\frac{\bar{y}_1y_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(\bar{q}_1+\bar{r}_1\big((1\!-\!\delta)y_2+\delta p_2\big)\Big) \Big(q_2+r_2\big((1\!-\!\delta)y_1+\delta q_1\big)\Big)}
      {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)} \times T,\\[1cm]

      v_{P}(s_1,s_2) &= &\displaystyle (1\!-\!\delta)\frac{\bar{y}_1\bar{y}_2}{1\!-\!\delta^2 r_1 r_2}+\delta \frac{\Big(\bar{q}_1+\bar{r}_1\big((1\!-\!\delta)y_2+\delta p_2\big)\Big) \Big(\bar{q}_2+\bar{r}_2\big((1\!-\!\delta)y_1+\delta p_1\big)\Big)}
      {\displaystyle(1\!-\!\delta r_1r_2)(1\!-\!\delta^2 r_1 r_2)} \times P.
      \end{array}
    \end{equation}

In these expressions, we have used the notation $r_i:=p_i\!-\!q_i$,
$\bar{y}_i\!=\!1\!-\!y_i$, $\bar{q}_i:=1\!-\!q_i$, and
$\bar{r}_i:=\bar{p}_i\!-\!\bar{q}_i=-r_i$ for $i\!\in\!\{1,2\}$.
\end{Prop}

\begin{proof}
Given a play between two reactive strategies with continuation probability
$\delta$. The outcome at turn \(t\) is given by,

\begin{equation}\label{eq:}
  (1 - \delta) \mathbf{v_0} \sum \delta^{t} M^{(t)},
\end{equation}

where $\mathbf{v_0}$ denotes the expected distribution of the four outcomes in
the very first round, and \(1- \delta\) the probability that the game ends.
It can be shown that,

@@

where \((1 - \delta)\mathbf{v_0}(I_4 - \delta M)^{-1}\) is vector \(\in R^{4}\)
and it the probabilities for being in any of the outcomes \(CC, CD, DC, DD\) in
the last round. Combining this with the payoff vector \(u\) and some algebraic
manipulation we derive to the Equation~\ref{Eq:LastRound}.
\end{proof}

In the updating stage we select a mutant and resident to be either the role
model or the learner. Assume the selected mutant. Given that they can interact
with only one other member of the population, they can interact either the
selected resident, another resident or with another mutant. The same is true for
the the selected resident. They can interact with the selected mutant, another
resident, or another mutant. Thus, in each updating stage there are five
possible combinations of pairs. These are illustrated by
Figure~\ref{fig:single_pairs}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.65\textwidth]{static/last_rounds_matches.tex}
  \caption{\textbf{Possible pairings combination in the updating stage, given
  that individuals interact with only one other member in the population.}. We
  distinguish between the selected resident and the rest of the residents and we
  do the same with the mutants. There is a probability that the selected
  resident interacts with the selected mutant.}\label{fig:single_pairs}
\end{figure}

@@

% In these expressions, we have used the notation $r_i:=p_i\!-\!q_i$,
% $\bar{y}_i\!=\!1\!-\!y_i$, $\bar{q}_i:=1\!-\!q_i$, and
% $\bar{r}_i:=\bar{p}_i\!-\!\bar{q}_i=-r_i$ for $i\!\in\!\{1,2\}$. Let
% $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round,
% and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector. Then
% one can show the following result.

### 2021-05-05 static/last_rounds_matches.tex
going over appendix

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{R} - S_{R}$}] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}

>>>>

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}
